Results

### 2018-08-01 4-results-simus.Rmd
analyze new results

@@

```{r, message=FALSE}
library(tidyverse)

methods.color <- setNames(
  c(scales::hue_pal()(6), c("black", "blue", "green")), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all", 
    "biglasso", "logit-simple-enet-ridge", "logit-simple-lasso")
) 
```

@@

  results.summary <- results %>%
    group_by_at(c(vars(starts_with("par")), "method")) %>%
    summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
    print(n = Inf)

@@

@@

```{r}
results1 <- list.files("results1", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()
```

@@

```{r}
results2 <- list.files("results2", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

results2.summary <- results2 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf) 
```

@@

```{r}
results2.summary %>%
  filter(grepl("logit", method)) %>%
  barplot_causal_one(h2 = 0.5) +
  facet_grid(par.model ~ par.dist)

@@

```{r}
results2.summary %>%
  filter(par.model == "fancy", method %in% c("logit-simple", "PRS-max")) %>%
  barplot_causal_all()

@@

```{r}
results2.summary %>%
  filter(par.model == "fancy", grepl("PRS", method)) %>%
  barplot_causal_all()

@@

@@

```{r}
results3 <- results2 %>%
  filter(par.model == "simple", method != "logit-triple")
```

@@

```{r}
results3.summary <- results3 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)
```

@@

```{r}
results4 <- list.files("results4", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

results4 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)

results34 <- rbind(
  cbind(simu = "all", results3),
  cbind(simu = "chr6", results4)
) %>%
  as_tibble()
```

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
             data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(par.model ~ par.causal) +
  facet_grid(par.h2 + par.dist ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

ggsave("figures/supp-AUC-chr6.pdf", scale = 1/110, width = 1153, height = 908)
```

@@

```{r}
results5 <- list.files("results5", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

results5.summary <- results5 %>%
  group_by_at(c(vars(starts_with("par")), "method", "n.train")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)

results35.summary <- results3.summary %>%
  filter(par.causal == "300 in all") %>%
  cbind.data.frame(n.train = 6000) %>%
  bind_rows(results5.summary)
```

```{r}
myggplot(results35.summary, aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
             data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  facet_grid(par.h2 ~ par.dist) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

@@

### Comparison with biglasso

```{r}
results7 <- list.files("results7", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()
```

```{r, fig.asp=0.65, out.width="95%", fig.width=16}
compare_logit(results7, "biglasso")

ggsave("figures/supp-biglasso.pdf", scale = 1/100, width = 1600, height = 1000)
```

### Comparison of different alpha values

```{r}
results8 <- list.files("results8", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()
```

```{r, fig.asp=0.65, out.width="95%", fig.width=16}
compare_logit(results8, c("logit-simple-enet-ridge", "logit-simple-lasso"))

ggsave("figures/supp-alpha.pdf", scale = 1/100, width = 1600, height = 1000)
```

>>>>

```{r}
library(tidyverse)
# devtools::install_github("privefl/bigsnpr")
library(bigsnpr)
# devtools::install_github("privefl/paper2-PRS/pkg.paper.PRS")
library(pkg.paper.PRS)  ## See code source for functions' code.
options(nboot = 1e4)
```

@@

```{r, message=FALSE}
COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)]), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all",
    "PRS-max-0.05", "PRS-max-0.2", "PRS-max-0.8")
) 
```

@@

  results.summary <- results %>%
    group_by_at(c(vars(starts_with("par")), "method")) %>%
    summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

@@

```{r, eval=FALSE}
G <- snp_attach("backingfiles/celiacQC_sub1.rds")$genotypes
corr <- snp_cor(G, size = 100)
saveRDS(corr, "backingfiles/corr2.rds")
```

```{r}
corr <- readRDS("backingfiles/corr2.rds")
```

@@

```{r}
results1 <- list.files("results1", full.names = TRUE) %>%
  read_format_results(corr)
```

@@

```{r}
results2 <- list.files("results2", full.names = TRUE) %>%
  read_format_results(corr)
```

@@

```{r}
results2 %>%
  filter(grepl("logit", method)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_one(h2 = 0.5) +
  facet_grid(par.model ~ par.dist)

@@

```{r}
results2 %>%
  filter(par.model == "fancy", method %in% c("logit-simple", "PRS-max")) %>%
  filter(thr.r2 == 0.2 | is.na(thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

@@

```{r}
results2 %>%
  filter(par.model == "fancy", grepl("PRS", method)) %>%
  filter(thr.r2 == 0.2 | is.na(thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

@@

### Different r2 thresholds

```{r}
results2 %>%
  filter(par.model == "simple", method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

ggsave("figures/main-AUC-all-r2.pdf", scale = 1/110, width = 1242, height = 951)
```

```{r}
results2 %>%
  filter(par.model == "simple", method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AltSens_mean = mean(AltSens), AltSens_boot = boot(AltSens), N = n()) %>%
  myggplot(aes(par.causal, AltSens_mean, fill = method, color = method)) + 
  geom_col(position = position_dodge(), alpha = 0.3) +
  geom_errorbar(aes(ymin = AltSens_mean - 2 * AltSens_boot,
                    ymax = AltSens_mean + 2 * AltSens_boot),
                position = position_dodge(width = 0.9), color = "black", width = 0.2) + 
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = "Causal SNPs (number and location)", y = "Mean of 100 AltSens",
       fill = "Method", color = "Method") +
  scale_fill_manual(values = methods.color) +
  scale_color_manual(values = methods.color) +
  facet_grid(par.dist ~ par.h2)

ggsave("figures/supp-AltSens-all-r2.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

```{r}
results3 <- results2 %>%
  filter(thr.r2 == 0.2 | is.na(thr.r2)) %>%
  filter(par.model == "simple", method != "logit-triple")
```

@@

```{r}
results3.summary <- results3 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

@@

```{r}
results4 <- list.files("results4", full.names = TRUE) %>%
  read_format_results(corr)
```

```{r, fig.asp = 1, out.width = "90%"}
results4 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

ggsave("figures/supp-AUC-chr6-all-r2.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

```{r}
results5 <- list.files("results5", full.names = TRUE) %>%
  read_format_results(corr)

results6 <- results2 %>%
  filter(par.model == "simple", par.causal == "300 in all") %>%
  bind_rows(results5) %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2))
```

```{r}
results6 %>%
  group_by_at(c(vars(starts_with("par")), "method", "n.train")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
             data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  facet_grid(par.dist ~ par.h2) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

@@
